Tabular Constraint Learning

### 2016-03-31 Paper/ECAI/tabular.tex
added files for the paper

\documentclass{ecai}
\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}

@@

\author{Name1 Surname1 \and Name2 Surname2 \and Name3 Surname3\institute{KU Leuven,
  Belgium, email: firstname.lastname@kuleuven} }

@@

\begin{abstract}
  abstract
  \end{abstract}
\section{Introduction}
test

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\documentclass{ecai}
\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage[dvipsnames]{xcolor}
\newcommand{\sergey}[1]{\textcolor{magenta}{{\sc Sergey} #1}\xspace}

@@

\author{Name1 Surname1 \and Name2 Surname2 \and Name3 Surname3 \institute{KU Leuven,Belgium, email: firstname.lastname@kuleuven} }

@@

\begin{abstract}
  abstract
  \end{abstract}
\section{Introduction}
\sergey{we need structure} test

\section{Related Work}
\sergey{what else should be in the related work?}
flashfill

sketch

tabular?

\bibliography{references}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
